ANOVA_MixedModel

### 2019-05-10 doc/MixedModel_PnD_Report.Rmd
moved some more files

@@

- use mouse average data
- only use house mouse data
- set Dom male as the intercept
- the sexes are matched (remove strains which don't have both sexes represented)

>>>>

Goals; complete 2 Mixed Model for
- house mouse
- Mus (with outgroups)

@@

- use mouse average data
- only use house mouse data
- set Dom male as the intercept
- the sexes are matched (remove strains which don't have both sexes represented)
- consider adding the stain most of the mouse data came from
